Computer Science House Constitution

### 2025-01-31 constitution.tex
more consistent language
formatting, clarify membership type
fix

\subsection{Abbreviations}
% Formatted as abbreviation  full term
\begin{tabular}{ l  l  l l l l}
	Chair   & \textit{Chairperson}            & Maintainer(s) & \textit{Constitutional Maintainer(s)} \\
	CSH     & \textit{Computer Science House} & OpComm        & \textit{Operational Communications}   \\
	E-Board & \textit{Executive Board}        & PR            & \textit{Public Relations}             \\
	Eval(s) & \textit{Evaluation(s)}          & R\&D          & \textit{Research and Development}     \\
	History & \textit{House History}          & ResLife       & \textit{Residence Life}               \\
	IMPs    & \textit{House Improvements}     & RTP(s)        & \textit{Root Type Person(s)}          \\
	Intro   & \textit{Introductory}           & Social        & \textit{Socials}                      \\                                  \\
\end{tabular}

@@

\begin{enumerate}
	\item A candidate for the OpComm Directorship shall be chosen by the current RTPs.
	\item The candidate is given a minimum of twenty-four hours to accept or decline the nomination.
	\item The candidate is presented to E-Board for approval.
	      This E-Board Meeting is closed to the E-Board Members, RTPs, and members with explicit invitation from E-Board.
	\item All Voting E-Board Members must be present during the discussion and voting period unless that member is a candidate for the position, in which case the member is absent and their vote is abstained.
	      An E-Board Vote is taken to determine whether the candidate is selected for the position.
\end{enumerate}

@@

\asection{Root Type Persons}
The OpComm Directorship is responsible for overseeing the implementation of maintenance and upgrades to the CSH computer systems networks.
It is a self-governing committee making decisions by Immediate Relative Majority vote with two-thirds quorum of current RTPs.
Membership is composed of all RTPs.

@@

\asubsubsection{Rules for Giving Exceptions and Exemptions for House Dues}
Members may appeal their situation to the Financial Director or E-board in the case that the member is dissatisfied with the Financial Director's decision.
The Financial Director, or E-board, then decides whether their situation warrants an extension to the payment deadline and/or reduction of the required dues.
\\*\\*
If the appeal is denied, the member’s payment is considered delinquent and the member’s privileges are revoked until payment can be made.
All dues must be collected in full before the annual Membership Eval, as defined in \ref{Membership Evaluation}.
After this date, dues collection is suspended until the start of the next academic year.
\asubsection{Breakdown of Dues for Directorship Budgets}
\begin{center}
	\begin{tabular}[c]{|l c|}
		\hline
		Directorship & Percentage of Dues
		\\ \hline
		\hline
		OpComm       & 20\%
		\\ \hline
		Social       & 20\%
		\\ \hline
		R\&D         & 20\%
		\\ \hline
		IMPs         & 15\%
		\\ \hline
		History      & 10\%
		\\ \hline
		Evals        & 5\%
		\\ \hline
		PR           & 5\%
		\\ \hline
		Accumulated  & 5\%
		\\ \hline
	\end{tabular}
\end{center}

>>>>

\subsection{Abbreviations}
% Formatted as abbreviation  full term
\begin{tabular}{ l  l  l l l l}
	Chair   & \textit{Chairperson}            & Maintainer(s) & \textit{Constitutional Maintainer(s)} \\
	CSH     & \textit{Computer Science House} & OpChomm        & \textit{Operational Communications}   \\
	E-Board & \textit{Executive Board}        & PR            & \textit{Public Relations}             \\
	Eval(s) & \textit{Evaluation(s)}          & R\&D          & \textit{Research and Development}     \\
	History & \textit{House History}          & ResLife       & \textit{Residence Life}               \\
	IMPs    & \textit{House Improvements}     & RTP(s)        & \textit{Root Type Person(s)}          \\
	Intro   & \textit{Introductory}           & Social        & \textit{Socials}                      \\                                  \\
\end{tabular}

@@

\begin{enumerate}
	\item A candidate for the OpChomm Directorship shall be chosen by the current RTPs.
	\item The candidate is given a minimum of twenty-four hours to accept or decline the nomination.
	\item The candidate is presented to E-Board for approval.
	      This E-Board Meeting is closed to the E-Board Members, RTPs, and members with explicit invitation from E-Board.
	\item All Voting E-Board Members must be present during the discussion and voting period unless that member is a candidate for the position, in which case the member is absent and their vote is abstained.
	      An E-Board Vote is taken to determine whether the candidate is selected for the position.
\end{enumerate}

@@

\asection{Root Type Persons}
The OpChomm Directorship is responsible for overseeing the implementation of maintenance and upgrades to the CSH computer systems networks.
It is a self-governing committee making decisions by Immediate Relative Majority vote with two-thirds quorum of current RTPs.
Membership is composed of all RTPs.

@@

\asubsubsection{Rules for Giving Exceptions and Exemptions for House Dues}
Members may appeal their situation to the Financial Director or E-board in the case that the member is dissatisfied with the Financial Director's decision.
The Financial Director, or E-board, then decides whether their situation warrants an extension to the payment deadline and/or reduction of the required dues.
\\*\\*
If the appeal is denied, the member’s payment is considered delinquent and the member’s privileges are revoked until payment can be made.
All dues must be collected in full before the annual Membership Eval, as defined in \ref{Membership Evaluation}.
After this date, dues collection is suspended until the start of the next academic year.
\asubsection{Breakdown of Dues for Directorship Budgets}
\begin{center}
	\begin{tabular}[c]{|l c|}
		\hline
		Directorship & Percentage of Dues
		\\ \hline
		\hline
		OpChomm       & 20\%
		\\ \hline
		Social       & 20\%
		\\ \hline
		R\&D         & 20\%
		\\ \hline
		IMPs         & 15\%
		\\ \hline
		History      & 10\%
		\\ \hline
		Evals        & 5\%
		\\ \hline
		PR           & 5\%
		\\ \hline
		Accumulated  & 5\%
		\\ \hline
	\end{tabular}
\end{center}
